### 2023-04-16 paper/elaboration.tex
brief description of PikaCore

\begin{align*}
  &\texttt{singleton} : (a \isA \layout{List}) \Ra \Int \ra a\\
  &\texttt{singleton}\; i := \textrm{Cons}\; i\; \textrm{Nil}
\end{align*}

@@

\begin{align*}
  &\texttt{singleton} : (a \isA \layout{List}) \Ra \Int \ra a\\
  &\texttt{singleton}\; [a]\; i := \apply_a(\textrm{Cons}\; i\; (\apply_a(\textrm{Nil})))
\end{align*}

\noindent
Elaboration will turn the first definition of \texttt{singleton} into the second definition.

>>>>

\begin{flalign*}
  &\texttt{singleton} : (a \isA \layout{\textrm{List}}) \Ra \Int \ra a\\
  &\texttt{singleton}\; i := \textrm{Cons}\; i\; \textrm{Nil}
\end{flalign*}

@@

\begin{flalign*}
  &\texttt{singleton} : (a \isA \layout{\textrm{List}}) \Ra \Int \ra a\\
  &\texttt{singleton}\; [a]\; i := \apply_a(\textrm{Cons}\; i\; (\apply_a(\textrm{Nil})))
\end{flalign*}

\noindent
Elaboration will turn the first definition of \texttt{singleton} into the second definition, using
a modified type inference algorithm. \Pika{} definitions must be fully elaborated before being
translated into \PikaCore.
